Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

This study employed a quantitative approach to address its research objectives. In order to fulfill them, we would need to collect a significant amount of data on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions that would generally known as colleges in other places, are simply called high schools, and provide
tertiary or associate degrees that do not have the same consideration as university degrees.}
To collect this data, two online surveys were designed and developed using Google Forms
in Spanish. These surveys consisted of six questions on demographic data
(such as sector, gender, degrees, discipline, age, or teaching experience)
followed by several multiple-choice questions allowing participants to choose multiple answers.

>>>>

This study employed a quantitative approach to address its research objectives. In order to fulfill them, we would need to collect a significant amount of data on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions that would generally known as colleges in other places, are simply called high schools, and provide
tertiary or associate degrees that do not have the same consideration as university degrees.}
In order to collect this data, two online surveys were designed and developed using Google Forms
in Spanish. These surveys consisted of six questions on demographic data
(such as sector, gender, degrees, discipline, age, or teaching experience)
followed by several multiple-choice questions allowing participants to choose multiple answers.
